Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2023-10-27 sections/combinatorial_semantics.tex
Puhsout in Hyp proof completed

Next $\sfrac{i_{1,V}}{\sim R_{V}} : V_{X} \to \sfrac{V_{X} + V_{Y}}{\sim R_{V}} = i_{1,V};s'$ where $s' : V_{X}+V_{Y} \to \sfrac{V_{X} + V_{Y}}{\sim R_{V}}$.
and 
$\sfrac{i_{1,E}}{\sim R_{E}} : E_{X} \to \sfrac{E_{X} + E_{Y}}{\sim R_{E}} = i_{1,E};s'$, similarly for $\sfrac{i_{2,E}}{\sim R_{E}}$ and $\sfrac{i_{2,V}}{\sim R_{V}}$.
We need to show
\begin{enumerate}
    \item $s_{X};(\sfrac{i_{1,V}}{\sim R_{V}})^{*}(e) = \sfrac{i_{1,E}}{\sim R_{E}};\sfrac{s_{X+Y}}{\sim (R_{V},R_{E})}(e)$
    \item $t_{X};(\sfrac{i_{1,V}}{\sim R_{V}})^{*}(e) = \sfrac{i_{1,E}}{\sim R_{E}};\sfrac{t_{X+Y}}{\sim (R_{V},R_{E})}(e)$
\end{enumerate}
and likewise for $i_{2}$.
Let's check the first one.
$s_{X};(\sfrac{i_{1,V}}{\sim R_{V}})^{*}(e) = s_{X};i_{1,V}^{*};s'^{*}(e)$ which is a homomorphism because $i_{1,V}$ and \update{$s'$ are}.

>>>>

Next $\sfrac{i_{1,V}}{\sim R_{V}} : V_{X} \to \sfrac{V_{X} + V_{Y}}{\sim R_{V}} = i_{1,V};s_1$.
and 
$\sfrac{i_{1,E}}{\sim R_{E}} : E_{X} \to \sfrac{E_{X} + E_{Y}}{\sim R_{E}} = i_{1,E};s_{E}'$, similarly for $\sfrac{i_{2,E}}{\sim R_{E}}$ and $\sfrac{i_{2,V}}{\sim R_{V}}$.
We need to show
\begin{enumerate}
    \item $s_{X};(\sfrac{i_{1,V}}{\sim R_{V}})^{*}(e) = \sfrac{i_{1,E}}{\sim R_{E}};\sfrac{s_{X+Y}}{\sim (R_{V},R_{E})}(e)$
    \item $t_{X};(\sfrac{i_{1,V}}{\sim R_{V}})^{*}(e) = \sfrac{i_{1,E}}{\sim R_{E}};\sfrac{t_{X+Y}}{\sim (R_{V},R_{E})}(e)$
\end{enumerate}
and likewise for $i_{2}$.
Let's check the first one for which we first need to check that $(s'_{E},s_{1})$ is a homomorphisms, i.e.
\[
s_{X+Y};s_1^{*}(e) = s'_{E};\sfrac{s_{X+Y}}{\sim (R_{V},R_{E})}(e) = \sfrac{s_{X+Y}}{\sim (R_{V},R_{E})}(s'_{E}(e)) = s_{X+Y};s_1^{*}(e)
\]
hence, $(\sfrac{i_{1,V}}{\sim R_{V}}, \sfrac{i_{1,E}}{\sim R_{V}})$ is a homomorphism because $(i_{1,V},i_{1,E})$ and $(s_1,s'_{E})$ are.
